Monte Carlo comparisons \\ VBSCAN Cost Action

### 2017-07-03 Setup/report.tex
Updated WHIZARD number with higher precision.

\subsection{ {\sc POWHEG}: Alexander Karlberg}
VBF approximation? \\
\subsection{ {\sc VBFNLO}: Michael Rauch}
VBF approximation \\
\subsection{ {\sc WHIZARD}: J\"urgen Reuter}
Full matrix element \\
\subsection{ \recola: Mathieu Pellen}
Full matrix element \\
\subsection{ \madgraph: Marco Zaro}
To be checked what is possible \\

@@

\begin{table}[h!]
    \begin{tabular}{c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
        {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
        {\sc Recola}  &  $1.5503 \pm 0.0003$ \\
        {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
        {\sc BONSAY}  &  $1.5524 \pm 0.0002$ \\
        {\sc MG5\_aMC}&  $1.547 \pm 0.001$   
    \end{tabular}
    \caption{\label{tab:LOrates} LO rates within VBS cuts from the different codes.}
\end{table}

>>>>

\subsection{ {\sc POWHEG}: Alexander Karlberg}
VBF approximation? \\
\subsection{ {\sc VBFNLO}: Michael Rauch}
VBF approximation \\
\subsection{ {\sc WHIZARD}: J\"urgen Reuter, Pascal Stienemeier}
Full matrix element \\
\subsection{ \recola: Mathieu Pellen}
Full matrix element \\
\subsection{ \madgraph: Marco Zaro}
To be checked what is possible \\

@@

\begin{table}[h!]
    \begin{tabular}{c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
        {\sc POWHEG}  &  $1.5573 \pm 0.0003$ \\
        {\sc Recola}  &  $1.5503 \pm 0.0003$ \\
        {\sc VBFNLO}  &  $1.5538 \pm 0.0002$ \\
        {\sc BONSAY}  &  $1.5524 \pm 0.0002$ \\
        {\sc WHIZARD} &  $1.5539 \pm 0.0004$ \\
        {\sc MG5\_aMC}&  $1.547 \pm 0.001$   
    \end{tabular}
    \caption{\label{tab:LOrates} LO rates within VBS cuts from the different codes.}
\end{table}
